### 2017-08-22 Documents/bootcamp_syllabus.tex
Updated Syllabus

There are two sections of this course,
one for undergrads (ECON-UB.0232) and one for MBA students (ECON-GB.2313).
The content is the same, but the schedules are different.

\subsubsection*{About the Instructor}
\href{http://www.waugheconomics.com}{Professor Michael Waugh} \\
Email: mwaugh@stern.nyu.edu\\
Office: KMC 7-74\\
Phone: 212-998-0288\\
Office hours: TBA, Monday and Wednesday.

\subsubsection*{Where and When}
Monday and Wednesday \\
%Section \#2: TISCH UC24, 3:30PM - 4:45PM

\subsection*{Requirements}

@@

This course has a strong {\bf support system\/} to help you when you run into problems ---
and anyone who codes runs into problems.
Each section has two teachers and a teaching assistant, all of them happy to answer your questions.
You can also post questions on our discussion group (see below).

@@

Eveything you need, including this document, is posted on
the {\bf course website\/}:
%
\vspace{-0.15in}
\begin{center}
\url{http://nyudatabootcamp.github.io/website/}
\end{center}
\vspace{-0.15in}
%
The {\bf book\/} has its own site,
\vspace{-0.15in}
\begin{center}
\url{https://www.gitbook.com/book/nyudatabootcamp/data-bootcamp/details}
\end{center}
\vspace{-0.15in}
%
There's a link to it on the course site.
We will not use NYU Classes.

We have set up {\bf announcement and discussion groups\/} (Google groups)
to make announcements and post questions. We will use this to post all assignments and
answer keys.
If you have coding or other questions, we encourage you to post them there.
If you know the answer to someone else's question, we {\bf strongly } encourage you to post that, too.
The links are
\vspace{-0.1in}
\begin{center}
UG:   \url{https://groups.google.com/forum/#!forum/nyu_data_bootcamp_ug}  \\
MBA:  \url{https://groups.google.com/forum/#!forum/nyu_data_bootcamp_mba}
\end{center}
\vspace{-0.1in}
%
You can access the same links from the course website.  Follow the instructions to join under whatever email address you plan to use.

@@

{\bf Write \& Review.\/}
After each topic, we recommend you:
% write everything you remember without looking
%at your notes or the book.  Note any gaps in your knowledge.
%Then read the book, work through the exercises, and fill in the gaps.
%Ask
%
%\begin{comment}
\begin{itemize}
\item {\it Write:\/}  Shortly after class, write down everything you remember
without looking at your notes or the book. Note things you don't understand --- gaps, we call them.
\item {\it Review:\/} Read the relevant section of the book.  Fill in the gaps. Ask for help with anything you still don't understand.
%\item {\bf Review:\/} Later on, go through what you wrote down earlier and  fill in the gaps
%by using the book.
\end{itemize}
%\end{comment}
%

@@

You can find answers to common questions on the course website.
You can also post questions on the discussion group;
see the link above and on the course website.
For others, email us (\href{mailto:nyu.databootcamp@gmail.com}{nyu.databootcamp@gmail.com}),
the co-teacher, or the teaching fellow; their contact information is on the course website.

@@

\input{../LaTeX/footer.tex}

>>>>

\subsubsection*{About the Instructor}
\href{http://www.waugheconomics.com}{Professor Michael Waugh} \\
Email: \href{mailto:mailto:mwaugh@stern.nyu.edu}{mwaugh@stern.nyu.edu}\\
Office: KMC 7-74\\
Phone: 212-998-0288\\
Office hours: TBA, Monday and Wednesday.

\subsubsection*{Where and When}
Meeting times: Monday and Wednesday 330-445pm\\

Meeting place: KMC 5-140

\section*{Requirements}

@@

This course has a strong {\bf support system\/} to help you when you run into problems|and anyone who codes runs into problems. We have a myself and a teaching fellow to help. Below is the contact info for our teaching fellow this semester.

\textbf{Teaching Fellows}\\
\\
Felipe Alves 
Email: \href{mailto:mailto:falves@stern.nyu.edu}{falves@stern.nyu.edu}\\
Office hours: TBA\\

Guess what\ldots you also have classmates that can help!!! You can post questions (and maybe answer your classmates questions) on our discussion group (see below). Felipe and I will also monitor the discussion group.

@@

Everything you need, including this document, is posted on
the {\bf course website\/}:
%
\vspace{-0.15in}
\begin{center}
\url{https://nyu.data-bootcamp.com/undergrad_outline/}
\end{center}
\vspace{-0.15in}
%
The {\bf book\/} has its own site,
\vspace{-0.15in}
\begin{center}
\url{https://www.gitbook.com/book/nyudatabootcamp/data-bootcamp/details}
\end{center}
\vspace{-0.15in}
%
There's a link to it on the course site.
We will not use NYU Classes.

We have set up {\bf announcement and discussion groups\/} (Google groups)
to make announcements and post questions. We will use this to post all assignments and
answer keys.
If you have coding or other questions, we encourage you to post them there.
If you know the answer to someone else's question, we {\bf strongly } encourage you to post that, too.
The links are
\vspace{-0.1in}
\begin{center}
\url{https://groups.google.com/d/forum/databootcamp_fall2017_undergrad} 
\end{center}
\vspace{-0.1in}
You can access the same links from the course website.  Follow the instructions to join under whatever email address you plan to use.

@@

{\bf Write \& Review.\/}
After each topic, we recommend you:
\begin{itemize}
\item {\it Write:\/}  Shortly after class, write down everything you remember
without looking at your notes or the book. Note things you don't understand|gaps, we call them.

\item {\it Review:\/} Read the relevant section of the book.  Fill in the gaps. Ask for help with anything you still don't understand.
\end{itemize}

@@

You can find answers to common questions on the course website. You can also post questions on the discussion group; see the link above and on the course website. For others, email me or the teaching fellow.

@@

%\input{../LaTeX/footer.tex}
